Equalizer: A Mature Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Add 2010 compositing paper
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@9 db7c848b-7755-4df2-b763-8796797afa52

@@

The region of interest is the screen-space 2D bounding box enclosing the
geometry rendered by a single resource. We have extended the core parallel
rendering framework to use an application-provided ROI to optimize the load
equalizer as well as image compositing performance. The load equalizer uses the
ROI to refine its load grid to the regions containing data. The compositing code
uses the ROI to minimize image readback and network transmission. In
\cite{EBAHMP:12}, we provide the details of the algorithm, and show that this
improves rendering performance of up to 25\%.

@@

GPU-CPU transfer plugins with optional compression (eg YUV) linked to CPU
compression for network transfer

>>>>

Qt is a popular window system with many application developers. Unfortunately,
it imposes a different threading model for window creation and event handling
then Equalizer. In Equalizer, each GPU rendering thread is independently
responsible for creating its windows, receiving the events and eventually
dispatching them to the application process main thread. This design is
motivated by the natural threading model of X11 and WGL, and allows simple
sequential semantics between OpenGL rendering and event handling. In contrast,
Qt requires all windows and QOpenGLContext to be created from the Qt main
thread. An existing Qt window or context may be moved to a different thread, and
events are signalled from the main thread.

@@

The region of interest is the screen-space 2D bounding box enclosing the
geometry rendered by a single resource. We have extended the core parallel
rendering framework to use an application-provided ROI to optimize the load
equalizer as well as image compositing performance. The load equalizer uses the
ROI to refine its load grid to the regions containing data. The compositing code
uses the ROI to minimize image readback and network transmission. In
\cite{MEP:10} and \cite{EBAHMP:12}, we provide the details of the algorithm, and
show that using ROI can quadruple the rendering performance, in particular for
the costly compositing step in sort-last rendering.

@@

GPU-CPU transfer plugins with optional compression (eg YUV) linked to CPU
compression for network transfer \cite{MEP:10}
